Equation-of-state insensitive relations after GW170817

### 2019-02-19 paper/bin-love-after-gw170817.tex
up to Sec. IIIB

EoS-insensitive relations can in fact be used for more than just measuring the nuclear EoS. For years, the theoretical physics community considered the possibility of using measurements of NS properties, like the mass, the radius and the moment of inertia, to constrain deviations from General Relativity in the strong-field regime. Certain modified theories of gravity, like scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-Aether and Horava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch}, beyond Horndesky theories~\cite{Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS. Yagi and Yunes solved this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}. Given a measurement of the Love number for a given NS, for example through GW observations, the I-Love-Q relations can be used to infer the moment of inertia or the quadrupole moment. A second independent measurement of either of these two quantities, for example through binary pulsar observations~\cite{Lattimer:2004nj} or observations with the Neutron star Interior Composition ExploreR (NICER)~\cite{Ozel:2015ykl}, then allows an EoS-insensitive test of General Relativity in the strong field regime~\cite{Yagi:ILQ}.

@@

Similar EoS-insensitive relations have been found between individual NS observables: the moment of inertia (I), the tidal deformability (Love), the quadrupole moment (Q), and the compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
These relations are EoS-insensitive to better than 1\% and 6\% respectively, and they have been important applications in both GW astrophysics and experimental relativity. For example, these relations and the measurement of the tidal deformabilities allow for the inference of several other stellar properties, such as the moment of inertia, the  compactness, the spin ($\chi$), and the radius of NSs~\cite{Kumar:2019xgp}.
Analyses such as that of~\cite{Kumar:2019xgp} could benefit from the improvement of such EoS-insensitive relations, which we derive in this paper.

@@

@@

Following~\cite{Yagi:ILQ}, we first fit the data for each EoS-insensitive relation to the following function:
\begin{equation}\label{eq:ILQfit}
\ln{y_i}=a_i+b_i \ln{x_i} + c_i (\ln{x_i})^2 + d_i (\ln{x_i})^3 + e_i (\ln{x_i})^4,
\end{equation}
where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and the updated coefficients are given in Table~\ref{tab:ILQfit}. This fitting function, however, does not limit properly to the Newtonian results~\cite{Yagi:ILQ}:
\begin{equation}\label{eq:Newtonian}
\bar{I}^{\text{N}} = K_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = K_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = K_{\bar{I}\bar{Q}}\bar{Q}^{2},
\end{equation}
where $\Lambda^{-1/5} \sim C$ when $C \ll 1$. One can thus improve the fitting function to 
\begin{equation}\label{eq:ILQfitNew}
y=K_{yx} x^{\alpha} \frac{1+\sum_{i=1}^3 a_i x^{-i/5}}{1+\sum_{i=1}^3 b_i x^{-i/5}},
\end{equation}
where $\alpha$ is either $2/5$, $1/5$, or $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations respectively, and where the new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}. While the two fits result in similar $R^2$ values\footnote{$R^2$ is the coefficient of determination, defined as $\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values} of $\sim 0.999995$, the fit in Eq.~\eqref{eq:ILQfitNew} has the advantage that it properly limits to the Newtonian result as $\Lambda \gg 1$~\cite{Yagi:binLove}.

{\ny{Too many tables. Please combine Tables 1 and 2 into a single table and change the notation of the fits appropriately.}}
\begin{table*}
\centering
\caption{
Updated fit parameters for the I-Love-Q relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
}\label{tab:ILQfit}
\begin{tabular}{ c  c | c c c c c } 
 \hline
 \hline
 $y_i$ & $x_i$ & $a_i$ & $b_i$ & $c_i$ & $d_i$ & $e_i$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $1.493$ & $0.06410$ & $0.02085$ & $-5.018 \times 10^{-4}$ & $3.16 \times 10^{-7}$ \\
 $\bar{Q}$ & $\Lambda$ & $0.2093$ & $0.07404$ & $-0.05382$ & $-5.018 \times 10^{-3}$ & $1.576 \times 10^{-4}$ \\ 
  $\bar{I}$ & $\bar{Q}$ & $1.383$ & $0.5931$ & $-0.02161$ & $0.04190$ & $-2.968 \times 10^{-3}$ \\
 \hline
 \hline
\end{tabular}
\end{table*}

\begin{table*}
\centering
\caption{
I-Love-Q and C-Love, relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
}\label{tab:ILQfitNew}
\begin{tabular}{ c  c  | c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313$ & $1.287$ & $0.09888$ & $-2.300$ & $-1.347$ & $0.3857$ & $-0.02870$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.555$ & $-2.122$ & $2.72$ & $-1.491$ & $0.8644$ & $-0.1428$ & $-1.397$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.008921$ & $10.59$ & $-37.46$ & $43.18$ & $-2.361$ & $1.967$ & $-0.5678$\\
 $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & $-383.5$ & $192.5$ & $-811.1$\\
\hline
\hline
\end{tabular}
\end{table*}

Figure~\ref{fig:ILQ} shows the improved I-Love-Q relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs.
Here, each category of EoS are fit individually using the curve found in Eq.~\ref{eq:ILQfitNew}.
We observe that the constrained EoSs show considerable improvement from the unconstrained EoSs.
Additionally, we note a large improvement from the results of previous works~\cite{Yagi:ILQ}.
This is validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained and constrained sets of EoSs.
Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q relation.

\begin{figure*}
\begin{center} 
\includegraphics[width=.32\textwidth]{IL.pdf}
\includegraphics[width=.32\textwidth]{QL.pdf}
\includegraphics[width=.32\textwidth]{IQ.pdf}
\end{center}
\caption{
Individual I-Love-Q relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew}.
Observe how the fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green).
}
\label{fig:ILQ}
\end{figure*}

\begin{table}
\centering
\caption{
Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference (the absolute difference is also shown in parenthesis for the C-Love, R-Love, and binary Love fits) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
 $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
 \hline
 \noalign{\smallskip}
\noalign{\smallskip}
 \noalign{\smallskip}
\noalign{\smallskip}
\hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 \multirow{2}{*}{$C-\Lambda$} & $0.065$ & $0.07198$ & $0.02169$\\
 & (--) & ($0.01837$) & ($0.006582$)\\
  \hline
 \multirow{2}{*}{$R-\Lambda$} & -- & $0.05649$ & $0.02172$\\
 & (--) & ($881.4 \text{ m}$) & ($358.9 \text{ m}$) \\
 \hline
 $\Lambda_a-\Lambda_s$ & $\sim0.50$ & $0.5724$ & $0.2140$\\
 $q=0.90$ & (--) & ($190.1$) & ($37.23$) \\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & $\sim0.20$ & $0.2447$ & $0.08284$\\
  $q=0.7$ & (--) & ($320.4$) & ($51.62$) \\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & $\sim0.025$ & $0.03841$ & $0.01823$\\
  $q=0.50$ & (--) & ($244.1$) & ($28.96$) \\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

These results indicate that EoS-insensitive relations can indeed be greatly improved upon by restricting to EoSs in agreeance with physical observations.
In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref.~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than was previously studied.
On the other hand, the constrained set of EoSs show significant improvement from that found in previous works.
This improvement can be beneficial to many future analyses, such as improvements to the constraints found on the moment of inertia, tidal deformability, compactness, spin, and radius found in Ref.~\cite{Kumar:2019xgp}.

@@

In this section, we investigate the I-Love-Q universality of hybrid stars, and their compatibility with their nuclear matter counterparts.
We consider three different sets of data to be fit by Eq.~\ref{eq:ILQfitNew}:
\begin{enumerate}
\item the complete set of 100 constrained EoSs combined with the 10 hybrid star EoSs,
\item the complete set of 100 constrained EoSs alone,
\item the complete set of 10 hybrid star EoSs alone.
\end{enumerate}
Following this, we compute the fractional difference from the fits for all three cases for the 10 hybrid star EoSs.
The fractional differences for the second case (fit to only the constrained EoSs) is shown by the dashed green lines in Fig.~\ref{fig:ILQ} for example.
For comparison purposes, Tab.~\ref{tab:hybridCompare} displays the maximal EoS variation in the $I-\Lambda$ relation for both the constrained and hybrid star EoSs in each case.

\begin{table}
\centering
\caption{
Comparison between the $I-\Lambda$ maximal EoS variability (fractional difference from the fit) for the constrained EoSs and the hybrid EoSs for three different cases of fitting data to Eq.~\ref{eq:ILQfitNew}: (1) fit to the combined data of constrained and hybrid EoS, (2) fit to the constrained EoS data alone, and (3) fit to the hybrid EoS data alone.
Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
The second case is demonstrated in Fig.~\ref{fig:ILQ}.
}\label{tab:hybridCompare}
\begin{tabular}{ c  || c c } 
 \hline
 \hline
 \textbf{Fitting} & \multicolumn{2}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-3}
 \textbf{Case} &  \multicolumn{1}{c|}{\emph{Constrained}} & \emph{Hybrid}\\
 \hline
 \emph{Combined} &  \multirow{2}{*}{$0.004407$} & \multirow{2}{*}{$0.01363$}\\
 \emph{(Case 1)} & &\\
 \cline{1-1}
 \emph{Constrained only} & \multirow{2}{*}{$0.003138$} & \multirow{2}{*}{$0.01736$}\\
  \emph{(Case 2)} & &\\
  \cline{1-1}
 \emph{Hybrid only} & \multirow{2}{*}{$0.008400$} & \multirow{2}{*}{$0.01017$}\\
  \emph{(Case 3)} & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

Observe how the hybrid star EoSs obey the I-Love-Q relations in each case by up to $\sim1.7$\%, slightly higher than that found for nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
Concluding, we claim that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed through nuclear EoS data, with a slight decrease in universality to $\sim1.7$\%.

>>>>

EoS-insensitive relations can in fact be used for more than just measuring the nuclear EoS. For years, the theoretical physics community considered the possibility of using measurements of NS properties, like the mass, the radius and the moment of inertia, to constrain deviations from General Relativity in the strong-field regime. Certain modified theories of gravity, like scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-Aether and Horava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch}, beyond Horndesky theories~\cite{Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS. Yagi and Yunes solved this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}. Given a measurement of the Love number for a given NS, for example through GW observations, the I-Love-Q relations can be used to infer the moment of inertia or the quadrupole moment. A second independent measurement of either of these two quantities, for example through binary pulsar observations~\cite{Lattimer:2004nj} or observations with the Neutron star Interior Composition ExploreR (NICER)~\cite{Ozel:2015ykl}, then allows an EoS-insensitive test of General Relativity in the strong field regime~\cite{Yagi:ILQ,Gupta:2017vsl}.

@@

Similar EoS-insensitive relations have been found between individual NS observables: the moment of inertia (I), the tidal deformability (Love), the quadrupole moment (Q), and the compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
These relations are EoS-insensitive to better than 1\% and 6\% respectively, and they have been important applications in both GW astrophysics~\cite{Kumar:2019xgp} and experimental relativity~\cite{Gupta:2017vsl}. For example, these relations and the measurement of the tidal deformabilities allow for the inference of several other stellar properties, such as the moment of inertia, the  compactness, the spin ($\chi$), and the radius of NSs~\cite{Kumar:2019xgp}.
Analyses such as that of~\cite{Kumar:2019xgp} could benefit from the improvement of such EoS-insensitive relations, which we derive in this paper.

@@

\begin{table*}[htb]
\centering
\begin{tabular}{ c  c  | c c c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $a_{4}$ & $a_{5}$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
  $\bar{I}$ & $\Lambda$ & (--) & (--) & $1.493$ & $0.06410$ & $0.02085$ & $-5.018 \times 10^{-4}$ & $3.16 \times 10^{-7}$ & (--) & (--) & (--)  \\
 $\bar{Q}$ & $\Lambda$ & (--) & (--) & $0.2093$ & $0.07404$ & $-0.05382$ & $-5.018 \times 10^{-3}$ & $1.576 \times 10^{-4}$ & (--)  &(--)  & (--) \\ 
  $\bar{I}$ & $\bar{Q}$ & (--) & (--) & $1.383$ & $0.5931$ & $-0.02161$ & $0.04190$ & $-2.968 \times 10^{-3}$ &(--)  &(--) & (--) \\
 \hline 
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313$ & $1.287$ & $0.09888$ & $-2.300$ & (--) & (--) & $-1.347$ & $0.3857$ & $-0.02870$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.555$ & $-2.122$ & $2.72$ & $-1.491$ & (--) & (--) & $0.8644$ & $-0.1428$ & $-1.397$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.008921$ & $10.59$ & $-37.46$ & $43.18$ &(--)  &(--)  & $-2.361$ & $1.967$ & $-0.5678$\\
 $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & (--) & (--) & $-383.5$ & $192.5$ & $-811.1$\\
\hline
\hline
\end{tabular}
\caption{
Fit parameters for the I-Love-Q and C-Love relations using the constrained set and the fitting functions in Eq.~\eqref{eq:ILQfit} (top) and in Eq.~\eqref{eq:ILQfitNew} (bottom).
}\label{tab:ILQfitNew}
\end{table*}

@@

Following~\cite{Yagi:ILQ}, we first fit the data for each EoS-insensitive relation to the following function:
\begin{equation}\label{eq:ILQfit}
\ln{y}=a_{1}+a_{2} \ln{x} + a_{3} (\ln{x})^2 + a_{4} (\ln{x})^3 + a_{5} (\ln{x})^4,
\end{equation}
where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and the updated coefficients are given in the top of Table~\ref{tab:ILQfitNew}. This fitting function, however, does not limit properly to the Newtonian results~\cite{Yagi:ILQ}:
\begin{equation}\label{eq:Newtonian}
\bar{I}^{\text{N}} = K_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = K_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = K_{\bar{I}\bar{Q}}\bar{Q}^{2},
\end{equation}
where $\Lambda^{-1/5} \sim C$ when $C \ll 1$. One can thus improve the fitting function to 
\begin{equation}\label{eq:ILQfitNew}
y=K_{yx} x^{\alpha} \frac{1+\sum_{i=1}^3 a_i x^{-i/5}}{1+\sum_{i=1}^3 b_i x^{-i/5}},
\end{equation}
where $\alpha$ is either $2/5$, $1/5$, or $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations respectively, and where the new fitting coefficients are presented in the bottom of Table~\ref{tab:ILQfitNew}. While the two fits result in similar $R^2$ values\footnote{$R^2$ is the coefficient of determination, defined as $\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values} of $\sim 0.999995$, the fit in Eq.~\eqref{eq:ILQfitNew} has the advantage that it properly limits to the Newtonian result as $\Lambda \gg 1$~\cite{Yagi:binLove}.

Figure~\ref{fig:ILQ} shows the improved I-Love-Q relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$. The fits are done using the new fitting function in Eq.~\eqref{eq:ILQfitNew} and over either the constrained set or the unconstrained set separately. The bottom panels show the relative fractional difference between the fit and the data for each set of EoSs. Observe that the new fits to the constrained set shows considerable more EoS-insensitivity than that fit to the unconstrained set. These results are summarized in Table~\ref{tab:maxVar}, which tabulates the maximum EoS variation in each fit. Clearly then, the EoS-insensitive relations can be made more universal by restricting the EoSs through the use of observations. Such improvements can be beneficial to future studies in GW astrophysics, such as those of~\cite{Kumar:2019xgp}, and in experimental relativity, such as those of~\cite{Gupta:2017vsl}.

\begin{figure*}[htb]
\begin{center} 
\includegraphics[width=.32\textwidth]{IL.pdf}
\includegraphics[width=.32\textwidth]{QL.pdf}
\includegraphics[width=.32\textwidth]{IQ.pdf}
\end{center}
\caption{
Individual I-Love-Q relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew}.
Observe how the fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green).
}
\label{fig:ILQ}
\end{figure*}

\begin{table}[htb]
\centering
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
 $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
 \hline
 \multirow{2}{*}{$C-\Lambda$} & $0.065$ & $0.07198$ & $0.02169$\\
 & (--) & ($0.01837$) & ($0.006582$)\\
  \hline
 \multirow{2}{*}{$R-\Lambda$} & -- & $0.05649$ & $0.02172$\\
 & (--) & ($881.4 \text{ m}$) & ($358.9 \text{ m}$) \\
 \hline
 $\Lambda_a-\Lambda_s$ & $\sim0.50$ & $0.5724$ & $0.2140$\\
 $q=0.90$ & (--) & ($190.1$) & ($37.23$) \\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & $\sim0.20$ & $0.2447$ & $0.08284$\\
  $q=0.7$ & (--) & ($320.4$) & ($51.62$) \\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & $\sim0.025$ & $0.03841$ & $0.01823$\\
  $q=0.50$ & (--) & ($244.1$) & ($28.96$) \\
  \cline{1-1}
\hline
\hline
\end{tabular}
\caption{Maximum relative and fractional EoS variation in the I-Love-Q, C-Love, R-Love, and binary Love relations using the unconstrained set, the constrained set and variations reported in previous work~\cite{Yagi:ILQ,Yagi:binLove}. The maximum absolute EoS variation is also reported in the C-Love, R-Love and binary Love cases in parenthesis. Observe that the maximum variation in the constrained set case is better than a factor of two smaller than the variability in the unconstrained case and in previous work. The maximum EoS variation in the unconstrained set is slightly larger than that found in previous work because the former is built from a large random sampling of EoSs. {\ny{Do we really need these many significant digits?}} 
}\label{tab:maxVar}
\end{table}

@@

Let us now focus on the I-Love-Q relations of hybrid stars, and their compatibility with their nuclear matter counterparts. For concreteness, we consider three different sets of EoSs in the hybrid case:
\begin{enumerate}
\item the complete set of 100 constrained EoSs combined with the 10 hybrid star EoSs,
\item the complete set of 100 constrained EoSs alone,
\item the complete set of 10 hybrid star EoSs alone.
\end{enumerate}
For each of these cases, we compute the I-Love-Q relations, we fit the data to Eq.~\eqref{eq:ILQfitNew} and we compute the relative fractional difference.

\begin{table}[htb]
\centering
\begin{tabular}{ c  || c c } 
 \hline
 \hline
 \textbf{Fitting} & \multicolumn{2}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-3}
 \textbf{Case} &  \multicolumn{1}{c|}{\emph{Constrained}} & \emph{Hybrid}\\
 \hline
 \emph{Combined} &  \multirow{2}{*}{$0.004407$} & \multirow{2}{*}{$0.01363$}\\
 \emph{(Case 1)} & &\\
 \cline{1-1}
 \emph{Constrained only} & \multirow{2}{*}{$0.003138$} & \multirow{2}{*}{$0.01736$}\\
  \emph{(Case 2)} & &\\
  \cline{1-1}
 \emph{Hybrid only} & \multirow{2}{*}{$0.008400$} & \multirow{2}{*}{$0.01017$}\\
  \emph{(Case 3)} & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\caption{
Maximum relative and fractional EoS variation in the I-Love relation, fitting to three different sets of data: using the constrained set plus hybrid EoSs, using the constrained set alone, EoS data alone, and using only the hybrid EoSs. In all 3 cases the hybrid EoSs are EoS-insensitive to $\sim1$\%, which is a slight decrease in universality relative to the hadronic only EoSs. {\ny{Do we really need these many significant digits?}}
}\label{tab:hybridCompare}
\end{table}

The fractional differences for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases. Observe how the hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:ILQ}. Observe also that the universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs. From this study, we conclude that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed with nuclear EoS data, albeit with a slight decrease in universality to $\sim1.7$\%.
